Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-04 trunk/paper.tex

@@

@@

\subsection{Workload Behavior Prediction}

>>>>

Based on our memory technology exploration, we now provide an overview of BROM
design. While many design methods envolved with new memory technologies endeavor
to reduce the off-chip memory access latency, this work focuses on minimize
off-chip bandwidth requirement by employing hybrid on-chip memory and
reconfiguration. For each level of memory, we select the memory technology that
has the highest provided bandwidth within given capacity. On top of such
hardware hierarchy design, we apply dynamic memory system reconfiguration with
the bandwidth demand of a specific set of applications as the major metric. One
desirable characteristic of BROM is that it provides prioritized access to the
residual memory capacity available at runtime instead of sharing it among all
data flows. By having control over the residual capacity, we can better utilize
the limited resources to enhance system performance. The hardware
reconfiguration is further facilitated by software prediction engine. Rather
than conventional last value predictors and table-based predictors, we employ a
probablity-based predictor that can achieve higher accuracy with small
performance overhead. The rest of this section describes the BROM design, which
is composed of on-chip memory hierarchy hardware design, the reconfiguration
mechanism, and the predictor engine.

@@

hardware design: num of levels; memory technology of each level; size of each level

reconfiguration support: how reconfigurable (Li -> Li+1 (Li+0.5); hardware
modification to support reconfiguration; what to do with reconfigured capacity

@@

decide size of each level si:

1) theoritical curves

2) bound:

- dbwi < pbwi -> si <= s1

- max throughput under power budget? -> si >= s2

- si <= hardware given max si

- si > si-1

reconfigure the unused capacity:

- if (> si): becomes si+1

- else: unused (or becomes lut)

\subsection{Prediction Engine}

statistical prediction

hierarchical prediction

performance opt: lut long enough but not too long (num of entries, bits per entry)
